\noindent Dear Reader,
\bigbreak

\pretolerance = 800
It nearly goes without saying that this past academic year has been difficult in a number of respects. One such difficulty was the transition to online schooling which proved to be at times a quite isolating experience. Though philosophy as a discipline proved to be relatively well-suited for virtual instruction, not being able to wander the halls of Dodd, getting into play-debates after class, was certainly a profound loss. 

Although the pandemic distanced us in these respects, it also equipped us with the tools to effectively communicate with our peers across the country. In the spirit of interconnectivity and combatting isolation, we redoubled our efforts to extend the submission pool beyond the Los Angeles area to schools across the country. As such, in this issue of Meditations we are proud to present works not just written by students at UCLA, but also those at NYU and Harvard. 

In the following we have the privilege of sharing four works, each of which focus on personal identity, examining how it’s formed, how it expresses itself, and what it leaves in its absence. Before offering these pieces however, it would be derelict not to extend thanks to our wonderful editors and submitters, without whom, none of this would be possible. A special thanks is also extended to the UCLA Philosophy Department for their support and resources throughout this process.

Without further ado, it is my great honor and pleasure to present to you this eighth edition of \textit{Meditations}. 


\bigbreak
\hfill
\begin{tabular}{@{}l@{}}
	Cheers,	\\
	\scshape Joshua Doland \\
	\textit{Editor-in-Chief}
\end{tabular}